Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-01-22 Paper/paper.tex
Update

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}

@@

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{qsos.pdf}
  \end{center}
  \caption{Quasar samples.}
  \label{fig:qsos}
\end{figure*}

%\clearpage
\subsection{Sample Homogenisation}
\label{sect:datahom}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
    %\includegraphics[height=0.88\textheight,keepaspectratio]{mosaic_small.pdf}
  \end{center}
  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.  The
    symbols show our inferred binned luminosity functions.  In each
    redshift bin, the black curve shows the best-fit double power law
    model, which is represented by the median of the posterior
    probability distribution function.  Yellow curves show a random
    draw from the posterior probability distribution function.  As
    discussed in the text, luminosity bins that show a decrease in the
    luminosity function at the faint end are deemed to be incomplete
    are are removed from our analysis while fitting the double power
    law model.  These bins are represented by open symbols in this
    figure.  Each panel shows the number of quasars in the respective
    redshift bin.  The number in parenthesis indicates the total
    number of quasars in the bin, before excluding incomplete
    bins. \textbf{[Remove redshift bins that were excluded from global
        analysis.]}}
  \label{fig:mosaic}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evol_28sep.pdf}
  \end{center}
  \caption{Parameter evolution from individual fits in
    Figures~\ref{fig:mosaic}.  Parameters from BOSS quasars are seen
    to be systematically offset.}
  \label{fig:evoln}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
  \end{center}
  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, the yellow
    curves show the best-fit double power law luminosity function in
    that redshift bin.  The green curves show the posterior
    distribution of the global model.  The global model agrees very
    well with the data in all redshift bins, except those spanned by
    BOSS, as BOSS quasars are excluded from the global analysis.}
  \label{fig:mosaic_global}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global_9oct.pdf}
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    model.  The symbols show the best fit parameters with 68\%
    uncertainties from the double power law fits to the data in
    redshift bins.  These points are identical to those in
    Figure~\ref{fig:evoln}, except that bins with BOSS qsos ($z\sim
    2$--$3$) are not shown.  In each panel, the black solid curve
    shows the best fit global model, and the coloured curves show a
    random sample drawn from the global posterior.}
  \label{fig:evoln_global}
\end{figure*}

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
  \end{center}
  \caption{AGN number density evolution in the global model.  Similar
    to Figure~\ref{fig:evoln_global}, symbols show the best fit
    parameters with 68\% uncertainties from the double power law fits
    to the data in redshift bins.  Black solid curve shows the best
    fit global model, and the coloured curves show a random sample
    drawn from the global posterior.  \textbf{[Show rejected bins in
        differnt symbols here.  Do not show the $-18$ case.  Cut the
        figure off at 6.5.]}}
  \label{fig:rhoqso}
\end{figure}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{emissivity_18_9oct.pdf}
    \includegraphics[width=0.5\textwidth]{emissivity_20_9oct.pdf}
    \end{tabular}
  \end{center}
  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
    Model luminosity functions are integrated down to $M_{1450}=-18$
    in the left panel and $-20$ in the right panel.  For comparison,
    various other published determinations of the 1~Ry emissivity of
    quasars are also shown in both panels of Figure~\ref{fig:e912}.
    The blue curve in these panels shows the AGN 1~Ry emissivity model
    of \citet{2012ApJ...746..125H}, which is very similar to the model
    of \citet{2007ApJ...654..731H}.  The red symbols with error bars
    show the determination from the fits of
    \citet{2015AA...578A..83G}.  The maroon curve is the published fit
    to the 1~Ry emissivity evolution in the fits of
    \citet{2017MNRAS.466.1160M}.  The green curve is the model of
    \citet{2015ApJ...813L...8M}.}
  \label{fig:e912}
\end{figure*}

@@

@@

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{g_18_10oct.pdf}
    \includegraphics[width=0.5\textwidth]{g_20_10oct.pdf}
    \end{tabular}
  \end{center}
  \caption{AGN contribution to the hydrogen photoionisation rate,
    assuming 100\% escape fraction.  Model luminosity functions are
    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
    the right panel.  The solid black curve shows the hydrogen
    photoionisate rate in our best-fit global model, and the yellow
    curves show a random sample from the global posterior.  The red
    points with error bars in this figure show the measurements of
    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
    forest, and the orange points show the measurements by
    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
    dashed green curve shows the hydrogen photoionisation rate
    evolution in the model of \citet{2012ApJ...746..125H}, while the
    solid green curve shows the contribution of quasars to it. }
  \label{fig:gammapi}
\end{figure*}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
  \end{center}
  \caption{Photon underproduction crisis.}
\end{figure}

@@

\citet{2014ApJ...789L..32K} reported that the hydrogen photoionization
rate required by simulations to match the observed HI column density
distribution and the effective Ly$\alpha$ opacity at low redshifts
($z\sim 0.1$) is a factor of five (check factor---it looks like about
ten in the plot) higher than that predicted by the model of
\citep{2012ApJ...746..125H}.  This deficit in the hydrogen
photoionization rate at these redshifts, termed `photon
underproduction crisis', has inspired models in which the excess
photonization in explained by blazars (citation) or an evolution in
the density structure of the IGM.  Subsequent simulations by
\citet{2015ApJ...811....3S}, calibrated the observed HI column density
distribution and the effective Ly$\alpha$ optical depth reduced the
severity of the problem by

\section{Conclusion}

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\usepackage{color}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{qsos.pdf}
    % data.py 
  \end{center}
  \caption{Quasar samples.}
  \label{fig:qsos}
\end{figure*}

@@

\subsection{Sample Homogenisation}
\label{sect:datahom}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
    % mosaic.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.  The
    symbols show our inferred binned luminosity functions.  In each
    redshift bin, the black curve shows the best-fit double power law
    model, which is represented by the median of the posterior
    probability distribution function.  Yellow curves show a random
    draw from the posterior probability distribution function.  As
    discussed in the text, luminosity bins that show a decrease in the
    luminosity function at the faint end are deemed to be incomplete
    are are removed from our analysis while fitting the double power
    law model.  These bins are represented by open symbols in this
    figure.  Each panel shows the number of quasars in the respective
    redshift bin.  The number in parenthesis indicates the total
    number of quasars in the bin, before excluding incomplete
    bins.}
  \label{fig:mosaic}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_individuals.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Parameter evolution from individual fits in
    Figures~\ref{fig:mosaic}.  Parameters from BOSS quasars are seen
    to be systematically offset.}
  \label{fig:evoln}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, the yellow
    curves show the best-fit double power law luminosity function in
    that redshift bin.  The green curves show the posterior
    distribution of the global model.  The global model agrees very
    well with the data in all redshift bins, except those spanned by
    BOSS, as BOSS quasars are excluded from the global analysis.}
  \label{fig:mosaic_global}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    model.  The symbols show the best fit parameters with 68\%
    uncertainties from the double power law fits to the data in
    redshift bins.  These points are identical to those in
    Figure~\ref{fig:evoln}, except that bins with BOSS qsos ($z\sim
    2$--$3$) are not shown.  In each panel, the black solid curve
    shows the best fit global model, and the coloured curves show a
    random sample drawn from the global posterior.}
  \label{fig:evoln_global}
\end{figure*}

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
    % rhoqso.py -- draw_withGlobal()
  \end{center}
  \caption{AGN number density evolution in the global model.  Similar
    to Figure~\ref{fig:evoln_global}, symbols show the best fit
    parameters with 68\% uncertainties from the double power law fits
    to the data in redshift bins.  Black solid curve shows the best
    fit global model, and the coloured curves show a random sample
    drawn from the global posterior. \gk{I still think we should show
      the $-18$ case here.}}
  \label{fig:rhoqso}
\end{figure}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
    \includegraphics[width=0.5\textwidth]{emissivity_21.pdf}
    % gammapi.py -- draw_emissivity() 
    \end{tabular}
  \end{center}
  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
    Model luminosity functions are integrated down to $M_{1450}=-18$
    in the left panel and $-20$ in the right panel.  For comparison,
    various other published determinations of the 1~Ry emissivity of
    quasars are also shown in both panels of Figure~\ref{fig:e912}.
    The blue curve in these panels shows the AGN 1~Ry emissivity model
    of \citet{2012ApJ...746..125H}, which is very similar to the model
    of \citet{2007ApJ...654..731H}.  The red symbols with error bars
    show the determination from the fits of
    \citet{2015AA...578A..83G}.  The maroon curve is the published fit
    to the 1~Ry emissivity evolution in the fits of
    \citet{2017MNRAS.466.1160M}.  The green curve is the model of
    \citet{2015ApJ...813L...8M}.}
  \label{fig:e912}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{g_18.pdf}
    \includegraphics[width=0.5\textwidth]{g_21.pdf}
    \end{tabular}
  \end{center}
  \caption{AGN contribution to the hydrogen photoionisation rate,
    assuming 100\% escape fraction.  Model luminosity functions are
    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
    the right panel.  The solid black curve shows the hydrogen
    photoionisate rate in our best-fit global model, and the yellow
    curves show a random sample from the global posterior.  The red
    points with error bars in this figure show the measurements of
    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
    forest, and the orange points show the measurements by
    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
    dashed green curve shows the hydrogen photoionisation rate
    evolution in the model of \citet{2012ApJ...746..125H}, while the
    solid green curve shows the contribution of quasars to it. \gk{Two
      problems to be addressed in these plots: (a) there is a
      contribution of $z>7$ qsos to the photoionisation rate at $z<7$
      but because our emissivity diverges at $z>7$, I had a to put an
      arbitrary cut-off; (b) the plots are too messy; we probably
      should show fewer things.}}
  \label{fig:gammapi}
\end{figure*}

@@

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
  \end{center}
  \caption{Photon underproduction crisis.\label{fig:puc}}
\end{figure}

@@

Our derivation of the LyC emissivity of AGN allows us to see if the
corresponding hydrogen photoionization rate is consistent with the
measured CDDF of the low-redshift ($z<0.5$) Ly$\alpha$ forest
\citep{2016ApJ...817..111D}.  \citet{2014ApJ...789L..32K} argued that
in order to match the CDDF observed by \citet{2016ApJ...817..111D} at
% Define acronym CDDF.
these redshifts, hydrodynamical cosmological simulations require a
hydrogen photoionization rate that is a factor of five larger than
that in the UV background (UVB) model of \citet{2012ApJ...746..125H}.
% This factor looks more than five in our plot!
Several recent studies in the literature have addressed this ``photon
underproduction crisis''.  On the one hand, these studies emphasised
the uncertainty in the \citet{2012ApJ...746..125H} UVB model at these
redshifts due to the lack of certainty in the UV photon emissivities
of galaxies and AGN \citep{2015MNRAS.451L..30K, 2015ApJ...811....3S}.
On the other hand, they noted the uncertainty in the results of the
cosmological simulations at these redshifts, due to effects such as
AGN feedback and limited numerical resolution
\citep{2015ApJ...811....3S, 2017MNRAS.467L..86V, 2017MNRAS.471.1056N,
  2017ApJ...837..106O, 2017MNRAS.466..838G, 2017MNRAS.467.3172G,
  2017ApJ...835..175G}.  A general conclusion of these studies was
that the discrepancy between the photoionization rate required by the
observed CDDF and predicted by the UVB model of
\citet{2012ApJ...746..125H} is likely to be smaller than that found by
\citet{2014ApJ...789L..32K}.  The discrepancy is about a factor of 2
instead of 5.

The black curve in Figure~\ref{fig:puc} shows the evolution of the
hydrogen photoionization rate due to AGN in our best-fit global
luminosity function model.  (Yellow shaded region around the black
curve shows the small 68\% uncertainty.)  We find that the
photoionisation rate in our model due to AGN alone is higher than that
in the \citet{2012ApJ...746..125H} UVB model by a factor of 2.  This
higher photoionisation rate is consistent with that derived by
\citet{2015MNRAS.451L..30K} using the quasar luminosity function
measurements of \citet{2009MNRAS.392...19C} and
\citet{2013A&A...551A..29P}.  It is also consistent with the
photoionization rate found by \citet{2017MNRAS.467.3172G}, who found
that this photoionisation rate is sufficient to explain the CDDF
measured by \citet{2016ApJ...817..111D}.

\section{Conclusions}
